\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\cite{AES2024security} IEEE Conference, ``On The Security of Advanced Encryption Standard (AES)," \textit{IEEE Xplore}, 2024. [Online]. Available: \url{https://ieeexplore.ieee.org/document/9826324}.

\cite{AESReview} NIST, ``Review of the Advanced Encryption Standard," \textit{NIST Publications}, 2023. [Online]. Available: \url{https://doi.org/10.6028/NIST.IR.8319}.

\cite{AESDevelopment} M. Smid, ``Development of the Advanced Encryption Standard," \textit{Journal of Research of the National Institute of Standards and Technology}, vol. 126, p. 18, 2021. [Online]. Available: \url{https://doi.org/10.6028/jres.126.024}.

\cite{AESXOR2025} IEEE Conference, ``File Encryption Using AES and XOR Algorithm for Data Security," \textit{IEEE Xplore}, 2025. [Online]. Available: \url{https://ieeexplore.ieee.org/document/10467936}.

\cite{pythonThreading} Python Software Foundation, ``threading — Thread-based parallelism," [Online]. Available: \url{https://docs.python.org/3/library/threading.html}. (visited on 01/16/2025).

\cite{pythonMultiprocessing} Python Software Foundation, ``multiprocessing — Process-based parallelism," [Online]. Available: \url{https://docs.python.org/3/library/multiprocessing.html}. (visited on 01/16/2025).

\cite{pythonTkinter} Python Software Foundation, ``tkinter — Python interface to Tcl/Tk," [Online]. Available: \url{https://docs.python.org/3/library/tkinter.html}. (visited on 01/16/2025).

\cite{pep371} Python Enhancement Proposal, ``PEP 371 – Addition of the multiprocessing package to the standard library," [Online]. Available: \url{https://peps.python.org/pep-0371/}. (visited on 01/16/2025).


\end{document}